---
title: "Homework 1"
author: "Andrew Blosse"
date: "2/2/21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

## Task 1

```{r mh_distance_function}
mh_distance <- function(x, y) {
  if (typeof(x) != typeof(y)) {
    warning("Vectors are not of the same type")
    return(-1)}
  else if (is.na(x) | is.na(y)) {
    warning("X or Y is NA")
    return(-1)}
   else if (is.nan(x) | is.nan(y)) {
    warning("X or Y is NaN")
    return(-1)}
   else if (is.infinite(x) | is.infinite(y)) {
    warning("X or Y is Inf/-Inf")
    return(-1)}
  else if (all(typeof(x) != c("logical", "character", "integer", "double"))) {
    warning("x is not logical/character/numeric")
    return(-1)}
  else if (all(typeof(y) != c("logical", "character", "integer", "double"))) {
    warning("y is not logical/character/numeric")
    return(-1)}
  else if (any(typeof(x)== c("character", "integer", "double")) | any(typeof(y)== c("character", "integer", "double"))) {
    if (nchar((as.character(x)))!= nchar((as.character(y)))) {
    warning("X and Y are not the same length")
    return(-1)}}
  
  else return(2)
}
mh_distance(T,F)
```
else if (nchar((as.character(x)))!= nchar((as.character(y)))) {
    warning("X and Y are not the same length")
    return(-1)}
else if (any(x == c(NA, NaN, Inf, -Inf))) {
      warning("x contains NA/NaN/Inf/-Inf values")
      return(-1)}
  #else if ((any(y==c(NA, NaN, Inf, -Inf)))) {
    #warning("y contains NA/NaN/Inf/-Inf")
    #return(-1)}


## Task 2

<i>
Be sure to remove chunk option `eval=FALSE` in the below code chunks
once you create `mh_distance()`. Do not include this italicized
text in your final submission.
</i>

**Initial test cases** (return a non-negative modified Hamming distance)

```{r}
mh_distance(x = "abc", y = "abc")
mh_distance(x = T, y = FALSE)
mh_distance(x = "523890", y = "752839")
mh_distance(x = 2341, y = 2350)
```

Added test cases that return a non-negative modified Hamming distance result.

```{r}
# additional test cases go here
```

**Initial test cases** (return values of `-1`)

```{r eval=FALSE}
mh_distance(x = 52, y = 113)
mh_distance(x = "swimming", y = "winning")
mh_distance(x = NA, y = TRUE)
mh_distance(x = 1.5, y = 2.5)
```

Added test cases that return a value of `-1`.

```{r}
# additional test cases go here
```


## Task 3

Consider the pair of vectors `s` and `w` given below.

```{r}
s <- c(26, 50123, 456.12, 8, 0)
w <- c(22, 50000, 451.00, 88, 0)
```

```{r}
# loop goes here
```


## Task 4

Brief write-up goes here...
