---
title: "Homework 1"
author: "Andrew Blosse"
date: "2/2/21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

## Task 1

```{r helperfunction}
mh <- function(x,y) {
  if (typeof(x) == "logical") {
    if (x != y) {
      return (1)}
    else return(0)}
  else if (typeof(x)=="character") {
    xlist <- unlist(strsplit(x, split = ""))
    ylist <- unlist(strsplit(y, split = ""))
    dis <- (xlist==ylist)
    return(length(dis)-sum(dis))}
  else if (any(typeof(x) == c("double","integer"))) {
    xdigits <- unlist(strsplit(as.character(x), split = ""))
    ydigits <- unlist(strsplit(as.character(y), split = ""))
    disn <- (xdigits == ydigits)
    return((length(disn)- sum(disn)))
  }
}

x <- 123
y<- 453
mh(x,y)
```

The above function calculates the modified Hamming distance in the event that x and y are acceptable inputs - it is not robust against incorrect inputs, which is why I call the above function within the below mh_distance function. Below, I've built in the necessary conditionals to return issue-specific errors if the user uses incorrect inputs. 

```{r mh_distance_function}

mh_distance <- function(x, y) {
  if (typeof(x) != typeof(y)) {
    warning("Vectors are not of the same type")
    return(-1)}
  else if (nchar(x) != nchar(y) & typeof(x) !="logical" &
           typeof(y)!="logical") {
    warning("x and y are different lengths")
    return(-1)
  }
  else if (is.na(x) | is.na(y)) {
    warning("x or y is NA")
    return(-1)}
   else if (is.nan(x) | is.nan(y)) {
    warning("x or y is NaN")
    return(-1)}
   else if (is.infinite(x) | is.infinite(y)) {
    warning("x or y is Inf/-Inf")
    return(-1)}
  else if (all(typeof(x) != c("logical", "character", "integer", "double"))) {
    warning("x is not logical/character/numeric")
    return(-1)}
  else if (all(typeof(y) != c("logical", "character", "integer", "double"))) {
    warning("y is not logical/character/numeric")
    return(-1)}
  else if (typeof(x)=="double" | typeof(y) == "double"){
    if (x %% 1 !=0 | y%%1 !=0) {
      warning("Decimals in x or y")
      return(-1)}
    else return(mh(x,y))}
  else return(mh(x,y))
}
```

## Task 2

**Initial test cases** (return a non-negative modified Hamming distance)

```{r}
mh_distance(x = "abc", y = "abc")
mh_distance(x = T, y = FALSE)
mh_distance(x = "523890", y = "752839")
mh_distance(x = 2341, y = 2350)
```

Added test cases that return a non-negative modified Hamming distance result.

```{r}
# additional test cases go here
mh_distance(1000000000000, 1000000000000) #function handles large values without issue
mh_distance("does it","recogni") #function recognizes spaces as characters
mh_distance(3L, 1L) #function is okay with integers
```

**Initial test cases** (return values of `-1`)

```{r eval=FALSE}
mh_distance(x = 52, y = 113)
mh_distance(x = "swimming", y = "winning")
mh_distance(x = NA, y = TRUE)
mh_distance(x = 1.5, y = 2.5)
```

Added test cases that return a value of `-1`.

```{r}
mh_distance(123, Inf) #function correctly identifies Inf/Inf
mh_distance(pi, 20) #function recognizes transcendental numbers
mh_distance(as.factor(1), 1) #function rejects factors and issues correct warning
```


## Task 3

Consider the pair of vectors `s` and `w` given below.

```{r}
s <- c(26, 50123, 456.12, 8, 0)
w <- c(22, 50000, 451.00, 88, 0)
```

```{r}
# loop goes here
```


## Task 4

Brief write-up goes here...
